Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-28 Article/main.tex
Update Article

\subsection{Collection of Case Studies and Determine Similarities}
As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description -the design principles followed were selected to be used. Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing and social engineering\cite{Sheng2007, Dincelli2020}. 
\\\\
The following step after finding these case studies was to identify their design principles and determine the major ones that most, if not all, made use of as well as how successful the game was found to be - which is determined in the individual publication either by trails of being judged by experts.

@@

\subsection{Case Studies and the Similarities in Design Principles}
Several case studies were examined in which some form of gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process. There are three main case studies that will be focused on in this study\cite{Dincelli2020,Sheng2007,allers2021children}.
\\\\
The first of these is titled, \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"} and focused on developing a gamified system to teach employees about security issues - focussing on social media and social engineering\cite{Dincelli2020}. 
\\\\
The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing that is done through the use of fake websites and the ways links are used for this\cite{Sheng2007}. 
\\\\
The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}
\begin{table}[htbp]
\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
\begin{adjustwidth}{-0.6cm}{}
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based	& Story-based 			& Clear and Simple Goals  \\
Reflection	& Reflection			& Quality of Feedback and Rewards  \\
	-		& Conceptual-Procedural & Structure of the Challenge  \\
	-		& 		-				& Motion-based Interaction  \\
	-		& 		-				& Simplicity  \\
\hline

>>>>

\subsection{Collection of Case Studies and Determine Similarities}
As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description - the design principles followed were selected to be used. Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing and social engineering\cite{Sheng2007, Dincelli2020}. 
\\\\
The following step after finding these case studies was to identify their design principles and determine the major ones that most, if not all, made use of as well as how successful the game was found to be - which is determined in the individual publication either by trails of being judged by experts.

@@

\subsection{Case Studies and the Similarities in Design Principles}
Several case studies were examined in which some form of gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process. There are three main case studies that will be focused on in this study\cite{Dincelli2020,Sheng2007,allers2021children}.
\\\\
%---------------No. 1
The first of these is titled, \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"} and focused on developing a gamified system to teach employees about security issues - focussing on social media and social engineering\cite{Dincelli2020}. 
\\\\
For the development of the artefact Dincelli and Chengalur-Smith\cite{Dincelli2020} made use of literature from instructional theory and gamification and as a result made use of a few key design principles. The first design principle followed is that the gamified system should make use of a \textit{story-based agent}\cite{Dincelli2020}. This means that a game should include some figure or character to guide users through the content as well as making use of story-telling in some capacity which is found to create curiosity within users\cite{Dincelli2020, Kapp2012a}. Furthermore, the use of a "choose your own adventure" style creates an interactive narrative by which the user is in control of certain decisions that change how the story plays out also improves learning\cite{Dincelli2020}. The second design principle used was that of \textit{reflection} which states that users should be given a moment of respite to dwell on what has previously been presented to them\cite{Dincelli2020,Sheng2007}.Feedback on various metrics of a users performance is also a design principle followed which allows for users to perform self evaluation\cite{Dincelli2020}. 
\\\\
The findings of this case study was that making use of a gamified system that used either visual stimuli or text were better at relaying information that traditional means and visual stimuli were better than text in terms of recognition, redintegration and ease of learning and they performed similarly in terms of recall, satisfaction and usability\cite{Dincelli2020}.
\\\\
%---------------No. 2
The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing that is done through the use of fake websites and the ways links are used for this\cite{Sheng2007}. 
\\\\
%---------------No. 3
The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}

\begin{table}[htbp]
\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
\begin{adjustwidth}{-0.0cm}{}
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based	& Story-based 			& Clear and Simple Goals  \\
Reflection	& Reflection			& Quality of Feedback and Rewards  \\
Feedback	& Conceptual-Procedural & Structure of the Challenge  \\
	-		& 		-				& Motion-based Interaction  \\
	-		& 		-				& Simplicity  \\
\hline
